---
title: "Visualizing Large Distributions"
author: "Poppy Huang"
date: "04-28-2022"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(nycflights13)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
```

## Background

_On-time data for all flights that departed NYC (i.e. JFK, LGA or EWR) in 2013. In this analysis we are going to look for carrier's relationship with arr_delay times._

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
ggplot(data = flights,
       aes(x = arr_delay)) + geom_bar(color = "blue")
```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

ggplot(data = flights) + 
  geom_point(mapping = aes(x = carrier, y = flight))
```
## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

ggplot(data = flights, 
       mapping = aes(x=carrier, 
                     y = arr_delay, 
                     color = arr_delay)) +
  geom_point(shape = 18)
```

## Conclusions

From what the 3 charts has showed, the first one shows that the delay normally falls into -30 to 100 mins, the most of the flights are on time.
The second chart shows how many flights has each carriers have in the year of 2013.
The last graph we can get some useful insights, seems AA, DL and MQ have some bigger problem with delaying flights. AS, UA and US are having less delaying flights.
